# Script for the Analysis of the data of the main Survey

Load the necessary packages and the data

```{r}
library(pacman)

p_load(
  tidyverse,
  openxlsx,
  psych,
  paran,
  stringr,
  ppcor,
  rstanarm,
  modelsummary
)

```

```{r}
data_path_ger = ".//Sources/MA_Erhebung_Deutsch_27.+Dezember+2023_07.52.csv"
data_path_eng = ".//Sources/MA_Erhebung_Prolific_27.+Dezember+2023_10.04.csv"

source("Scripts/pre_processing.R")
```


# Items Statistics

```{r}
items_no_kern$internal_similarity%>%describe()
'   vars  n  mean   sd median trimmed  mad min max range skew kurtosis  se
X1    1 77 74.53 7.03     73   74.21 5.93  61  89    28 0.47    -0.68 0.8'

items_no_kern$train_similarity%>%describe()
'   vars  n  mean   sd median trimmed  mad min max range skew kurtosis   se
X1    1 77 75.88 5.51     75    75.6 5.93  65  89    24 0.38    -0.46 0.63'

```



# Demographics

```{r}
data$country %>% table() %>%prop.table()
# Distribution by Country (Count):
# England: 99
# Germany: 48

# Distribution by Country (Percentage):
# England: 67.3%
# Germany: 32.7%


data$utm_source%>%table() %>%prop.table()%>%round(3)*100


# Source of participants (Count):
# Whatsapp: 22
# Facebook: 6
# Instagram: 4
# LinkedIn: 16

# Source of participants (Percentage):
# Whatsapp: 45.8%
# Facebook: 12.5%
# Instagram: 8.3%
# LinkedIn: 33.3%

data$Q125 %>% factor(levels = c(1,2,3,4,5,6,7),labels = c("17 oder jünger","18-20","21-29","30-39","40-49","50-59","60 oder älter"))%>% table() %>%prop.table()

# Age Distribution (Count):
# 17 or younger: 0
# 18-20: 3
# 21-29: 51
# 30-39: 30
# 40-49: 25
# 50-59: 24
# 60 or older: 14

# Age Distribution (Percentage):
# 17 or younger: 0.0%
# 18-20: 2.0%
# 21-29: 34.7%
# 30-39: 20.4%
# 40-49: 17.0%
# 50-59: 16.3%
# 60 or older: 9.5%


data$Q126 %>% factor(levels = c(1,2,3,4),labels = c("weiblich","männlich","Ich möchte keine Zuordnung vornehmen.","divers"))%>% table() %>%prop.table()%>%round(3)*100

# Gender Distribution (Count):
# Female: 78
# Male: 66
# Prefer not to specify: 0
# Non-binary: 3

# Gender Distribution (Percentage):
# Female: 53.1%
# Male: 44.9%
# Prefer not to specify: 0.0%
# Non-binary: 2.0%


data$SQ06 %>% factor(levels = c(1,2,3,4,5,6),labels = c("Hochschulabschluss","Fachhochschulabschluss","Fachhochschulreife/ Abitur","Mittlere Reife","Hauptschulabschluss","kein Abschluss"))%>% table() %>%prop.table()%>%round(3)*100

# Education Level                               Count   Percentage
# --------------------------------------------------------------
# University Degree                               27        56.2
# University of Applied Sciences Degree            5        10.4
# University Entrance Qualification / Abitur       14        29.2
# Intermediate Education (High School)             2         4.2
# Secondary School Certificate                      0         0.0
# No Education                                     0         0.0


data$Q22%>% factor(levels = c(2,4,5,7,8,9),labels = c("Completed primary school education","Completed secondary school education","Vocational school or similar","University, Bachelors degree","University or professional degree (MA, MS, MBA, PhD, JD, MD, DDS)","None"))%>% table() %>%prop.table()%>%round(3)*100

'                               Completed primary school education 
                                                                1 
                             Completed secondary school education 
                                                               24 
                                     Vocational school or similar 
                                                               17 
                                     University, Bachelors degree 
                                                               44 
University or professional degree (MA, MS, MBA, PhD, JD, MD, DDS) 
                                                               13 
                                                             None 
                                                                0'


# Do you work?
data$SQ09 %>% factor(levels = c(1,0),labels = c("Ja","Nein"))%>% table() %>%prop.table()%>%round(3)*100
# Employment Status (Count):
# Yes: 116
# No: 31

# Employment Status (Percentage):
# Yes: 78.9%
# No: 21.1%

# Working hours
data$SQ09_1_1 %>% describe()

'   vars   n mean    sd median trimmed   mad min max range  skew kurtosis   se
X1    1 147 25.4 16.31     31   26.03 14.83   1  47    46 -0.39    -1.44 1.35'
```



# Compare english and german data

```{r}
sum_values_ger <- colMeans(data[data$country=="Germany",13:114])
sum_values_en <- colMeans((data[data$country=="England",13:114]))

cor.test(sum_values_ger,sum_values_en,method = "pearson")


```



# Select Items for the scales


```{r}
fa_ocean <- fa(ocean_ai_gen, nfactors = 5, rotate = "oblimin", fm = "pa")
print(fa_ocean, digits = 2, sort = TRUE, cut = 0.2)
# " I do not like to be of service to others." 0.23

ocean_ai_gen_2 <- ocean_ai_gen[,-5]

fa_ocean_2 <- fa(ocean_ai_gen_2, nfactors = 5, rotate = "oblimin", fm = "pa")
print(fa_ocean_2, digits = 2, sort = TRUE, cut = 0.2)
# " I feel little compassion for those who are worse off than myself." 0.35

ocean_ai_gen_3 <- ocean_ai_gen_2[,-2]

fa_ocean_3 <- fa(ocean_ai_gen_3, nfactors = 5, rotate = "oblimin", fm = "pa")

print(fa_ocean_3, digits = 2, sort = TRUE, cut = 0.2)
#" I am the type of person who is willing to compromise in conflicts." 0.37

ocean_ai_gen_4 <- ocean_ai_gen_3[,-6]

fa_ocean_4 <- fa(ocean_ai_gen_4, nfactors = 5, rotate = "oblimin", fm = "pa")

print(fa_ocean_4, digits = 2, sort = TRUE, cut = 0.2)
# " I see myself as someone who is not very interested in abstract ideas." 0.38

ocean_ai_gen_5 <- ocean_ai_gen_4[,-38]

fa_ocean_5 <- fa(ocean_ai_gen_5, nfactors = 5, rotate = "oblimin", fm = "pa")

print(fa_ocean_5, digits = 2, sort = TRUE, cut = 0.2)

# " I try to impose my will on others." -0.42, 0.39

ocean_ai_gen_6 <- ocean_ai_gen_5[,-3]

fa_ocean_6 <- fa(ocean_ai_gen_6, nfactors = 5, rotate = "oblimin", fm = "pa")

print(fa_ocean_6, digits = 2, sort = TRUE, cut = 0.3)
```

# Get the Item names 

```{r}

items_efa_ocean <- items$item[c(27,28,22,29,24,26,21,25,23,30,6,9,10,8,3,5,7,2,4,1,12,11,17,20,14,18,15,13,19,16,37,36,33,40,39,31,47,46,44,42,43,45)]

```




```{r}
ocean_ai_gen_a <- ocean_ai_gen_a[,colnames(ocean_ai_gen_a)%in%colnames(ocean_ai_gen_6)]
ocean_ai_gen_o <- ocean_ai_gen_o[,colnames(ocean_ai_gen_o)%in%colnames(ocean_ai_gen_6)]

```

# Itemselektion Need for Closure

```{r}
fa_nfc <- fa(nfc, nfactors = 1, rotate = "oblimin", fm = "pa")
print(fa_nfc, digits = 2, sort = TRUE)
#item 69, V22, Loading: 0.03

nfc_2 <- nfc[,-22]

fa_nfc_2 <- fa(nfc_2, nfactors = 1, rotate = "oblimin", fm = "pa")
#need_for_closure.Q4_63	16	0.11	

nfc_3 <- nfc_2[,-16]

fa_nfc_3 <- fa(nfc_3, nfactors = 1, rotate = "oblimin", fm = "pa")

print(fa_nfc_3, digits = 2, sort = TRUE)
# need_for_closure.Q4_71	22	0.16	

nfc_4 <- nfc_3[,-22]

fa_nfc_4 <- fa(nfc_4, nfactors = 1, rotate = "oblimin", fm = "pa")

print(fa_nfc_4, digits = 2, sort = TRUE)
# need_for_closure.Q4_74	24	0.26	

nfc_5 <- nfc_4[,-24]

fa_nfc_5 <- fa(nfc_5, nfactors = 1, rotate = "oblimin", fm = "pa")

print(fa_nfc_5, digits = 2, sort = TRUE)
# need_for_closure.Q4_72	22	0.25

nfc_6 <- nfc_5[,-22]

fa_nfc_6 <- fa(nfc_6, nfactors = 1, rotate = "oblimin", fm = "pa")

print(fa_nfc_6, digits = 2, sort = TRUE)
# need_for_closure.Q4_75	23	0.25

nfc_7 <- nfc_6[,-23]

fa_nfc_7 <- fa(nfc_7, nfactors = 1, rotate = "oblimin", fm = "pa")

print(fa_nfc_7, digits = 2, sort = TRUE)
# need_for_closure.Q4_73	22	0.28	

nfc_8 <- nfc_7[,-22]

fa_nfc_8 <- fa(nfc_8, nfactors = 1, rotate = "oblimin", fm = "pa")

print(fa_nfc_8, digits = 2, sort = TRUE)
# need_for_closure.Q4_61	14	0.32	

nfc_9 <- nfc_8[,-14]

fa_nfc_9 <- fa(nfc_9, nfactors = 1, rotate = "oblimin", fm = "pa")

print(fa_nfc_9, digits = 2, sort = TRUE)
# need_for_closure.Q4_76	21	0.35	

nfc_10 <- nfc_9[,-21]

fa_nfc_10 <- fa(nfc_10, nfactors = 1, rotate = "oblimin", fm = "pa")

print(fa_nfc_10, digits = 2, sort = TRUE)
# need_for_closure.Q4_77	21	0.38

nfc_11 <- nfc_10[,-21]

fa_nfc_11 <- fa(nfc_11, nfactors = 1, rotate = "oblimin", fm = "pa")

print(fa_nfc_11, digits = 2, sort = TRUE, cut = .3)

# 69, 63, 71, 74, 72, 75, 73, 61, 76, 77

nfc_items_removed <- items$item[c(69,63,71,74,72,75,73,61,76,77)] 
nfc_items <- items$item[c(70,54,66,59,48,57,49,51,58,56,67,60,50,53,62,55,64,65,52,68)]
```







# Create Scale Means

```{r}

ocean_a_mean <- apply(ocean_ai_gen_a,1,mean)
ocean_c_mean <- apply(ocean_ai_gen_c,1,mean)
ocean_e_mean <- apply(ocean_ai_gen_e,1,mean)
ocean_o_mean <- apply(ocean_ai_gen_o,1,mean)
ocean_n_mean <- apply(ocean_ai_gen_n,1,mean)

nfc_mean <- apply(nfc_3,1,mean)

bfi_10_a_mean <- apply(bfi_10_a,1,mean)
bfi_10_c_mean <- apply(bfi_10_c,1,mean)
bfi_10_e_mean <- apply(bfi_10_e,1,mean)
bfi_10_o_mean <- apply(bfi_10_o,1,mean)
bfi_10_n_mean <- apply(bfi_10_n,1,mean)

nfc_kern_mean <- apply(nfc_kern,1,mean)

scale_means <- data.frame(ocean_a_mean = ocean_a_mean,
                          ocean_c_mean = ocean_c_mean,
                          ocean_e_mean = ocean_e_mean,
                          ocean_o_mean = ocean_o_mean,
                          ocean_n_mean = ocean_n_mean,
                          nfc_mean = nfc_mean,
                          bfi_10_a_mean = bfi_10_a_mean,
                          bfi_10_c_mean = bfi_10_c_mean,
                          bfi_10_e_mean = bfi_10_e_mean,
                          bfi_10_o_mean = bfi_10_o_mean,
                          bfi_10_n_mean = bfi_10_n_mean,
                          nfc_kern_mean = nfc_kern_mean)
```

# create correlation tables for a descriptive summary

```{r}
p_load(pdist)

de_ids <- which(data$country=="Germany")
en_ids <- which(data$country!="Germany")

scale_means_kern <- scale_means[,c(6:11)]
scale_means_no_kern <- scale_means[,-c(6:11)]



group_corr_toal_kern <- cor(scale_means_kern)
group_corr_total_no_kern <- cor(scale_means_no_kern)

describe(c(group_corr_toal_kern))

# Mean correlation r =.15, sd = .46, Md = .12

describe(c(group_corr_total_no_kern))

# Mean correlation r =.17, sd = .46, Md = .12

diff <- (group_corr_toal_kern-group_corr_total_no_kern)
diff <- abs((diff))

describe(c(diff))
# mean r_diff = 0.29, sd 0.23


mean(group_means_total_no_kern)

group_means_de_kern <- apply(scale_means_kern[de_ids,],MARGIN = 2,mean)
group_means_de_no_kern <- apply(scale_means_no_kern[de_ids,],MARGIN = 2,mean)

group_means_en_kern <- apply(scale_means_kern[en_ids,],MARGIN = 2,mean)
group_means_en_no_kern <- apply(scale_means_no_kern[en_ids,],MARGIN = 2,mean)

group_sd_de_kern <- apply(scale_means_kern[de_ids,],MARGIN = 2,sd)
group_sd_de_no_kern <- apply(scale_means_no_kern[de_ids,],MARGIN = 2,sd)

group_sd_en_kern <- apply(scale_means_kern[en_ids,],MARGIN = 2,sd)
group_sd_en_no_kern <- apply(scale_means_no_kern[en_ids,],MARGIN = 2,sd)






corr_data_kern <- data.frame("M DE" = group_means_de_kern,"group_sd_de" = group_sd_de_kern,"group_means_en" = group_means_en_kern,"group_sd_en" = group_sd_en_kern)

corr_data_no_kern <- data.frame("M DE" = group_means_de_no_kern,"group_sd_de" = group_sd_de_no_kern,"group_means_en" = group_means_en_no_kern,"group_sd_en" = group_sd_en_no_kern)

'datasummary_correlation(scale_means_kern,add_columns = corr_data_kern,output = "Corr_Mat_1_kern.docx" )


datasummary_correlation(scale_means_no_kern,add_columns = corr_data_no_kern,output = "Corr_Mat_1_no_kern.docx" )'







```

## H2 Convergent Validity

```{r}

# Function for calculating the correlation test statistic

calculate_z_value <- function(r,n){
  r <- r-.4
  t_value <- r*sqrt((n-2)/(1-r^2))
  return(t_value)
}

# Check for normality of scales

cor.plot(scale_means)

car::qqPlot(scale_means$ocean_n_mean,main = "KI-Neurotizismus")
car::qqPlot(scale_means$bfi_10_n_mean,main = "BFI-10-Neurotizismus")

describe(scale_means$ocean_n_mean)
# Skew = 0.13, kur = -0.55

describe(scale_means$bfi_10_n_mean)
# s = 0.25, k = -0.55

car::qqPlot(scale_means$ocean_a_mean,main = "KI-Verträglichkeit")
car::qqPlot(scale_means$bfi_10_a_mean,main = "BFI-10-Verträglichkeit")

describe(scale_means$ocean_a_mean)
# s = -1.08, k = 1.55

describe(scale_means$bfi_10_a_mean)
# s = -0.7, k =  0.74

car::qqPlot(scale_means$ocean_c_mean,main = "KI-Gewissenhaftigkeit")
car::qqPlot(scale_means$bfi_10_c_mean,main = "BFI-10-Gewissenhaftigkeit")

describe(scale_means$ocean_c_mean)
# s = -0.47, k -0.44

describe(scale_means$bfi_10_c_mean)
# s -0.44, k -0.29

car::qqPlot(scale_means$ocean_e_mean,main = "KI-Extraversion")
car::qqPlot(scale_means$bfi_10_e_mean,main = "BFI-10-Extraversion")

describe(scale_means$ocean_e_mean)
# S = -0.22, k = -0.64

describe(scale_means$bfi_10_e_mean)
# s = -0.07, k = -0.8

car::qqPlot(scale_means$ocean_o_mean,main = "KI-Offenheit")
car::qqPlot(scale_means$bfi_10_o_mean,main = "BFI-10-Offenheit")

describe(scale_means$ocean_o_mean)
# s = -0.41, k = -0.26

describe(scale_means$bfi_10_o_mean)

# s = -0.24, k = -0.51

car::qqPlot(scale_means$nfc_mean,main = "KI-NFC")
car::qqPlot(scale_means$nfc_kern_mean,main = "NFC-Kern")

describe(scale_means$nfc_mean)
# s = -0.73, k = 1.53


## Neuroticism

corr.test(scale_means$ocean_n_mean,scale_means$bfi_10_n_mean,method = "pearson", ci= TRUE)%>% print(short = FALSE,digits = 3)
# r = .89; 95% CI: (.85, .92); 

# z value
calculate_z_value(r = cor(scale_means$ocean_n_mean,scale_means$bfi_10_n_mean,method = "pearson"),n = 147)
#6.736507

pnorm(q = 6.736507, lower.tail = FALSE)%>%round(3)
# p <.001

## Agreeableness

corr.test(scale_means$ocean_a_mean,scale_means$bfi_10_a_mean,method = "pearson", ci= TRUE)%>% print(short = FALSE,digits = 3)
# r = .63, 95% CI: (.52, .72); p < .001

# z value

calculate_z_value(r = cor(scale_means$ocean_a_mean,scale_means$bfi_10_a_mean,method = "pearson"),n = 147)
# 2.877373

pnorm( q = 2.877373, lower.tail = FALSE)%>%round(3)
# p = .002

## Conscientiousness

corr.test(scale_means$ocean_c_mean,scale_means$bfi_10_c_mean,method = "pearson", ci= TRUE)%>% print(short = FALSE,digits = 3)
# r = .74, 95% CI: (.66, .81); p < .001

# z value

calculate_z_value(r = cor(scale_means$ocean_c_mean,scale_means$bfi_10_c_mean,method = "pearson"),n = 147)
# 4.355044

pnorm(q = 4.355044, lower.tail = FALSE)%>%round(3)

# p < .001


## Extraversion

corr.test(scale_means$ocean_e_mean,scale_means$bfi_10_e_mean,method = "pearson", ci= TRUE)%>% print(short = FALSE,digits = 3)
# r = .89, 95% CI: (.85, .92); p < .001

# z value

calculate_z_value(r = cor(scale_means$ocean_e_mean,scale_means$bfi_10_e_mean,method = "pearson"),n = 147)

# 6.729625

pnorm(q = 6.729625, lower.tail = FALSE)%>%round(3)

# p < .001


## Openness

corr.test(scale_means$ocean_o_mean,scale_means$bfi_10_o_mean,method = "pearson", ci= TRUE)%>% print(short = FALSE,digits = 3)
# r = .49, 95% CI: (.35, .60); p < .001

# z value

calculate_z_value(r = cor(scale_means$ocean_o_mean,scale_means$bfi_10_o_mean,method = "pearson"),n = 147)
# 1.038441

pnorm(q = 1.038441, lower.tail = FALSE)%>%round(3)
# p = .15

## NFC

corr.test(scale_means$nfc_mean,scale_means$nfc_kern_mean,method = "pearson", ci= TRUE)%>% print(short = FALSE,digits = 3)
# r = .89, 95% CI: (.85, .92);

# z value

calculate_z_value(r = cor(scale_means$nfc_mean,scale_means$nfc_kern_mean,method = "pearson"),n = 147)
# 6.780933;

pnorm( q = 6.780933, lower.tail = FALSE)%>%round(3)

# p < .001

```

# Implementation of the Spearman-Brown formula
```{r}

# Source: https://m-py.github.io/TesttheorieR/psychometrie.html
## Define a SPEARMAN-BROWN function. It takes two arguments:
## (a) a reliability estimator
## (b) an extension factor

spearman_brown <- function(reliability, factor) {
    numerator  <- reliability * factor
    denominator <- 1 + (factor-1) * reliability
    corrected_reliability <- numerator / denominator
    return(corrected_reliability)
}
```



## Calculate Alpha

```{r}
alpha(nfc_kern)
# Alpha = .86, 95% CI: (.82, .89); mean_r = .29

alpha(nfc_3)
# Alpha = .93, 95% CI: (.91, .94); mean_r = .32

alpha(ocean_ai_gen_o,check.keys = TRUE)
# Alpha = .78, 95% CI: (.72, .83); mean_r = .38

alpha(ocean_ai_gen_c,check.keys = TRUE)
# Alpha = .82, 95% CI: (.77, .86); mean_r = .31

alpha(ocean_ai_gen_e, check.keys = TRUE)
# Alpha = .91, 95% CI: (.88, .93); mean_r = .48

alpha(ocean_ai_gen_a, check.keys=TRUE)
# Alpha = .79, 95% CI: (.74, .84); mean_r = .40

alpha(ocean_ai_gen_n, check.keys=TRUE)
# Alpha = .92, 95% CI: (.90, .94);mean_r = .53

## Neuroticism
(corr.test(bfi_10_n,ci=TRUE)%>% print(short = FALSE,digits = 3))
# r = .64, 95% CI: (.53, .73); p < .001

spearman_brown(reliability = cor(bfi_10_n[,1],bfi_10_n[,2]),factor = 5)
# 0.8985481 

# 2.5% CI

spearman_brown(reliability = corr.test(bfi_10_n[,1],bfi_10_n[,2],ci=TRUE)$ci$lower,factor = 5)
# 0.8505688

# 97.5% CI

spearman_brown(reliability = corr.test(bfi_10_n[,1],bfi_10_n[,2],ci=TRUE)$ci$upper,factor = 5)
# 0.929797

## Agreeableness

(corr.test(bfi_10_a,ci=TRUE)%>% print(short = FALSE,digits = 3))
# r = .22, 95%CI: (.06, .37); p = .008

spearman_brown(reliability = cor(bfi_10_a[,1],bfi_10_a[,2]),factor = 3)
# 0.4555848

# 2.5% CI

spearman_brown(reliability = corr.test(bfi_10_a[,1],bfi_10_a[,2],ci=TRUE)$ci$lower,factor = 3)
#0.1565625

# 97.5% CI

spearman_brown(reliability = corr.test(bfi_10_a[,1],bfi_10_a[,2],ci=TRUE)$ci$upper,factor = 3)
#0.6349864

## Conscientiousness

(corr.test(bfi_10_c,ci=TRUE)%>% print(short = FALSE,digits = 3))
# r = .47, 95% CI: (.34, .59); p < .001

spearman_brown(reliability = cor(bfi_10_c[,1],bfi_10_c[,2]),factor = 5)
# 0.8185848

# 2.5% CI

spearman_brown(reliability = corr.test(bfi_10_c[,1],bfi_10_c[,2],ci=TRUE)$ci$lower,factor = 5)
# 0.7189521

# 97.5% CI

spearman_brown(reliability = corr.test(bfi_10_c[,1],bfi_10_c[,2],ci=TRUE)$ci$upper,factor = 5)
# 0.8783641

## Extraversion

(corr.test(bfi_10_e,ci=TRUE)%>% print(short = FALSE,digits = 3))
# r = .70, 95% CI: (.60, .77); p < .001

spearman_brown(reliability = cor(bfi_10_e[,1],bfi_10_e[,2]),factor = 5)
# 0.919935

# 2.5% CI

spearman_brown(reliability = corr.test(bfi_10_e[,1],bfi_10_e[,2],ci=TRUE)$ci$lower,factor = 5)
# 0.8836028

# 97.5% CI

spearman_brown(reliability = corr.test(bfi_10_e[,1],bfi_10_e[,2],ci=TRUE)$ci$upper,factor = 5)
# 0.9441171

## Openness

(corr.test(bfi_10_o,ci=TRUE)%>% print(short = FALSE,digits = 3))
# r = .38, 95% CI: (.23, .51); p < .001

spearman_brown(reliability = cor(bfi_10_o[,1],bfi_10_o[,2]),factor = 3)
# 0.643115

# 2.5% CI

spearman_brown(reliability = corr.test(bfi_10_o[,1],bfi_10_o[,2],ci=TRUE)$ci$lower,factor = 3)
#0.4686061

# 97.5% CI

spearman_brown(reliability = corr.test(bfi_10_o[,1],bfi_10_o[,2],ci=TRUE)$ci$upper,factor = 3)
#0.7547635


```
# Calculation of results for feedback to participants

```{r}
data$ocean_o_mean <- bfi_10_o %>% rowMeans()
data$ocean_c_mean <- bfi_10_c %>% rowMeans()
data$ocean_e_mean <- bfi_10_e %>% rowMeans()
data$ocean_a_mean <- bfi_10_a %>% rowMeans()
data$ocean_n_mean <- bfi_10_n %>% rowMeans()

data$nfc_mean <- nfc_kern %>% rowMeans()

user_data <- data%>%
  filter(ErgebnisseYN == 1)%>%
  filter(!is.na(Q13))%>%
  dplyr::select(ocean_o_mean,ocean_c_mean,ocean_e_mean,ocean_a_mean,ocean_n_mean,nfc_mean,Q13, UserID)


#  save(user_data,file = "user_results.RData")

```